Does the COMPAS Needle Always Point Towards Equity? Finding Fairness in the COMPAS Risk Assessment Algorithm':' A Case Study

### 2022-04-14 Paper_Draft2/Draft2.Rmd

```{r race plot, echo=FALSE, fig.align='center', fig.cap= 'This plot shows the distribution of defendant races.', out.width= "500px", out.height= "300px"}
knitr::include_graphics("../images/race_bar_plot.png")
```

```{r age plot, echo=FALSE, fig.align='center', fig.cap= 'This plot shows the distribution of defendant ages by race.', out.width= "500px", out.height= "300px"}
knitr::include_graphics("../images/race_age_plot.png")
```

```{r recid plot, echo=FALSE, fig.align='center', fig.cap= 'This plot shows the distribution of two year recidivism outcomes.', out.width= "500px", out.height= "300px"}
knitr::include_graphics("../images/recid_bar_plot.png")
```

```{r recid race plot,echo=FALSE, fig.align='center', fig.cap= 'This plot shows the distribution of two year recidivism outcomes by race.', out.width= "500px", out.height= "300px"}
knitr::include_graphics("../images/race_recid_plot.png")
```

@@

# Discussion

# Conclusion

>>>>

```{r race plot, echo=FALSE, fig.align='center', fig.cap= 'The race distribution for black people is 3000 and the distribution for white people is 2100. Therefore, there are more black people in the dataset than white people.', out.width= "500px", out.height= "300px"}
knitr::include_graphics("../images/race_bar_plot.png")
```

```{r age plot, echo=FALSE, fig.align='center', fig.cap= "This plot is a Kernel Density Estimate (KDE) plot. The y-axis represents the KDE of the Probability Distribution Function of the age variable in our dataset. The probability of a defendant's age being between two points on the x-axis is the total shaded area of the curve under the two points. The purple dotted line shows the average age of Black defendants and the green dotted line shows the average age of white defendants. For both groups, the majority of defendants are relatively young, but this is especially noticeable for Black defendants.", out.width= "500px", out.height= "300px"}
knitr::include_graphics("../images/race_age_plot.png")
```

```{r recid plot, echo=FALSE, fig.align='center', fig.cap= 'Of both black and white people, there is a higher percentage of people who did not recidivate than who did. 2500 people recidivated, whereas approximately 2600 did not.', out.width= "500px", out.height= "300px"}
knitr::include_graphics("../images/recid_bar_plot.png")
```

```{r recid race plot,echo=FALSE, fig.align='center', fig.cap= 'When we divide the data into Black and white defendants, we can see that Black defendants recidivate more than white defendants. Black defendants recidivate are more likely than not to recidivate. However, we can also see that there are more Black defendants in the dataset in general.', out.width= "500px", out.height= "300px"}
knitr::include_graphics("../images/race_recid_plot.png")
```

@@

### 2022-04-14 Paper_Draft2/Draft2.tex

\caption{This plot shows the distribution of defendant races.}\label{fig:race plot}
\end{figure}

@@

\caption{This plot shows the distribution of defendant ages by race.}\label{fig:age plot}
\end{figure}

@@

\caption{This plot shows the distribution of two year recidivism outcomes.}\label{fig:recid plot}
\end{figure}

@@

\caption{This plot shows the distribution of two year recidivism outcomes by race.}\label{fig:recid race plot}
\end{figure}

@@

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

\hypertarget{conclusion}{%
\section{Conclusion}\label{conclusion}}

>>>>

\caption{The race distribution for black people is 3000 and the distribution for white people is 2100. Therefore, there are more black people in the dataset than white people.}\label{fig:race plot}
\end{figure}

@@

\caption{This plot is a Kernel Density Estimate (KDE) plot. The y-axis represents the KDE of the Probability Distribution Function of the age variable in our dataset. The probability of a defendant's age being between two points on the x-axis is the total shaded area of the curve under the two points. The purple dotted line shows the average age of Black defendants and the green dotted line shows the average age of white defendants. For both groups, the majority of defendants are relatively young, but this is especially noticeable for Black defendants.}\label{fig:age plot}
\end{figure}

@@

\caption{Of both black and white people, there is a higher percentage of people who did not recidivate than who did. 2500 people recidivated, whereas approximately 2600 did not.}\label{fig:recid plot}
\end{figure}

@@

\caption{When we divide the data into Black and white defendants, we can see that Black defendants recidivate more than white defendants. Black defendants recidivate are more likely than not to recidivate. However, we can also see that there are more Black defendants in the dataset in general.}\label{fig:recid race plot}
\end{figure}

@@
